\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[hidelinks]{hyperref}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Alexander Ulanov}}\\
	Saint Petersburg $\cdot$ alexander.ulanov@gmail.com $\cdot$ +79043334469 $\cdot$ \url{https://www.linkedin.com/in/alexanderulanov/} $\cdot$ \url{https://t.me/aulanov}\\
\end{center}

%==== Experience ====%
Software developer with 15 years of experience, team lead with 7 years of experience. Hands-on experience in FX volatility derivatives pricing. C\#, Kotlin, C++ with focus on quality, strong analytical skills.

\vspace{3mm}
%==== Experience ====%
\header{Employment History}
\vspace{1mm}

\textbf{Deutsche Bank} \quad \url{https://www.db.com/} \hfill Saint Petersburg\\
\textit{Software Developer Engineer} \hfill June 2017 - Present\\
\vspace{1mm}
Project: Automatic FX volatility calibration to broker, exchange and internal data. Data capturing, calibration and distribution system, streaming volatility for automated trading in Autobahn FX Options \\
\vspace{1mm}
Project: Viewing and managing electronic liquidity in the FX option market \\
\vspace{1mm}
Responsibilities:
\begin{itemize} \itemsep 1pt
	\item Developed and designed FX options volatility marking system and it\textquotesingle{}s subsystems including UI tools (C\#, Kotlin, C++)
    \item Direct communication with trading desk (business), including requirements analysis, support
    \item Maintained and onboarded new option volatility sources (CME/ETF/etc.)
    \item Managed team of 4 members
\end{itemize}
Key achievements:
\begin{itemize} \itemsep 1pt
	\item Developed unified volatility model in pricing flows used in FX derivatives desk
    \item Optimized pricing engine which led up to 4x performance
    \item Designed and implemented microservice architecture for various new services.
\end{itemize}
Technologies: C\# $\cdot$ Kotlin $\cdot$ C++ $\cdot$ WinForms $\cdot$ WPF $\cdot$ Spring $\cdot$ Kafka $\cdot$ Solace $\cdot$ Consul $\cdot$ Oracle $\cdot$ kdb+ $\cdot$ ClickHouse \\
\vspace{3mm}
\textbf{Kappa Engineering} \quad \url{https://www.kappaeng.com} \hfill UK, London\\
\textit{Lead Software Engineer} \hfill Mar 2012 - June 2017\\
\vspace{1mm}
Greenfield project: Application for analyzing outcomes from hundreds of multi-fractured horizontal wells. Designed architecture and core components. Managed team of 3 members. \\
Technologies: C\# $\cdot$ WinForms $\cdot$ SQL Server $\cdot$ Prism \\
\vspace{3mm}
\textbf{Devexperts} \quad \url{https://devexperts.com} \hfill Saint Petersburg\\
\textit{Software Developer} \hfill Nov 2009 - Jan 2012\\
\vspace{1mm}
Project: Real-time administrative management tool for the FX market. The system tracks a thousand updates per second, displaying results in tables / charts, providing comprehensive monitoring and ability to manage players on the market in real-time. \\
Technologies: C\# $\cdot$ WinForms $\cdot$ Oracle $\cdot$ SQLite $\cdot$ Prism $\cdot$ Rx  \\
\vspace{3mm}
\textbf{Saint Petersburg State University} \hfill Saint Petersburg\\
\textit{Senior Lecture}, Part time, Remote \hfill Sep 2009 - Present\\

\vspace{3mm}
\textbf{Zed} \quad \url{https://www.zed.com} \hfill Saint Petersburg\\
\textit{Software Developer} \hfill Aug 2007 - Nov 2009\\
\vspace{1mm}
Project: Web-based application for managing the billing system of the company's SMS services. Created the communication protocol between company and mobile operators like Tele2, MTS, Beeline, and Megafon. \\
Technologies: C\# $\cdot$ Java $\cdot$ ASP.NET $\cdot$ Oracle $\cdot$ SQL Server \\
\vspace{3mm}
%==== Education ====%
\header{Education}
\textbf{World Quant University} \quad \url{https://www.wqu.edu} \\
MS Financial Engineering \textit{GPA: 96\%} \hfill Jan 2020 - June 2022\\
Thesis: Practical aspects of American option pricing Implementation \\
\vspace{2mm}
\textbf{Saint Petersburg State University} \quad \url{https://apmath.spbu.ru} \\
Specialist degree in Mathematics \textit{GPA: 4.86 of 5, magna cum laude} \hfill Sep 2004 - Jun 2009\\
Thesis: Patent search with feedback from users \\
\vspace{2mm}

%==== Hobbies ====%
\header{Hobbies}
	Swimmer, triathlete, fond of folk music\\
\vspace{2mm} 
\end{document}